Title?

### 2016-07-25 draft.tex
Modified tex file to be phys rev style.

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{slashed}
\usepackage{graphicx}
\usepackage{feynmf}
\graphicspath{ {images/} }
\setlength{\parindent}{10ex}

@@

@@

Considering first the pp diagrams, each of the $p-p-\pi $ vertices contribute a factor of $ i\gamma_5 g_{pp}$ , where $g_{pp}$ is the pseudoscalar pion-nucleon coupling. $f_{pp}$, the pseudovector pion-nucleon coupling, is related by $ g_{pp} = \frac{2M_N}{m_\pi} f_{pp} $. The internal  pion line contributes a factor of $\frac{-i}{\mathcal{L}^2 - m_\pi^2}$, where $ \mathcal{L} $ is the appropriate exchange momentum.  The two outgoing nucleons each contribute a spinor $ \bar{u}(p_i)$, and the two incoming nucleons contribute a spinor $u(p_i)$. The outgoing boson A with momentum $q_a$ contributes a polarization vector $\epsilon^\mu$, and the $ p-p-A $ vertex contributes $e\epsilon \gamma_\mu$. The internal fermion line, between the $p-p-\pi$ vertex and the $p-p-A$ vertex, contributes a factor of \[ -i\frac{\slashed p_5 + M_N}{p_5^2-M^2_N} \] where $p_5$ is the momentum of the internal fermion. Considering diagram 2 as an example, we have $p_5 = q_a + p_3$, and so $p_5^2 = p_5 \cdot p_5 = q_a^2 + p_3^2 + 2 (q_a \cdot p_3)$, and the factor from the fermion line becomes \[ -i\frac{\slashed p_i \pm \slashed q_a + M_N}{m_A^2 \pm 2 q_a \cdot p_i} \] where the index labels which of the nucleons attaches to the A boson, while the plus sign corresponds to diagrams where it attaches right of the pion vertex, and the minus to diagrams where it attaches left of the pion vertex. Labeling them from one to eight, with the exchange diagrams given odd labels and the direct given even labels, the matrix elements are then
		 \[ M_1 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed{\epsilon} u(p_1)\]
%
	 	\[ M_2 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p3) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed \epsilon  u(p_1) \]
	%
	 	\[ M_3 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \epsilon  u(p_2) \]
%
	 	\[ M_4 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \epsilon  u(p_2) \]
%	
		 \[ M_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
			 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \slashed{\epsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2)\]
			 %
		\[ M_6 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \slashed{\epsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2)\]
			 		 %
 		 \[ M_7 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \slashed{\epsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1)\]
			 		 		 %
		\[ M_8 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
		}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1)\]
		%
	where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and $ f_{pp} $ is the pseudovector pion-nucleon coupling.

	The amplitude is then \[  \sum_{spins} \mathcal{M}^2 = \sum_{spins}|M_2+M_4+M_6+M_8-M_1-M_3-M_5-M_7|^2  \]. At this point the calculation diverges from the axionic bremsstrahlung calculation: in the region of the mass of the A boson is not necessarily negligible. The kinematic relations are thus \[ 
	p_1 \cdot p_2 = M_N^2 - \frac{l^2}{2} - \frac{k^2}{2} + p_2 \cdot q_a\]
	 \[p_1 \cdot p_3 = M_N^2 + k \cdot l - \frac{k^2}{2} + p_3 \cdot q_a\]  
	 \[p_1 \cdot p_4 = k \cdot l + M_N^2 - \frac{l^2}{2} + p_4 \cdot q_a \]
	 \[p_2 \cdot p_3 = M_N^2 - \frac{l^2}{2} \]
 	 \[p_2 \cdot p_4 = M_N^2 - \frac{k^2}{2} \]
 	 \[p_3 \cdot p_4 = k \cdot l + M_N^2 - \frac{l^2 + k^2}{2} \]
 	 Unfortunately, with these relations it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression contains some two hundred and fifty terms.

 	 For the pn interaction the calculation proceeds similarly, with the only new matrix element coming from diagram five, bremsstrahlung off the internal pion 
 	 \[ M_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \epsilon}{l^2-m_\pi^2
 	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \epsilon \]
	This amplitude too is unwieldy.

@@

	\[ Q_i = \int (2\pi)^4 E_A \sum_{spins} \mathcal{M}^2_i f(p_1) f(p_2)\delta(p_1+p_2-p_3-p_4-q_a) dLIPS \]
	Here $ E_A $ is the energy of the emitted boson, and $ f(p) $ are the initial occupation numbers. The nucleons in the core are comfortably non-degenerate and non-relativistic, so  the Pauli blocking factor is omitted and the Maxwell-Boltzmann distribution used  \[ f(p) =  \frac{n_b}{2} (\frac{2 \pi}{M_N T})^{3/2} e^{-\frac{\textbf{p}^2} {2 M_N T}} \]

	This integration is performed numerically to obtain $ Q_i $, which is the rate of energy emission per unit volume associated with either the pn or pp process. To obtain the dark gauge boson luminosity, it is assumed that production takes place in a core volume of radius 1 km, so $ \mathcal{L}_A = V(Q_{pp} + Q_{pn}) $. $ \mathcal{L}_A $ is a complicated function of $ m_A $ and $ T $, but is simply proportional to the square of the parameter $ \epsilon $; pulling that out of the expression gives a constraint \[ \epsilon^2 I_A(m_A, T) \le \mathcal{L}_\nu \] or a bound on the coupling of \[ \epsilon \le \sqrt{\frac{4.1 * 10^{37} MeV^2}{I_A(m_A, T)}} \] and the exclusion region is generated by varying the mass.

	\subsection{Decay limit}
	The constraint from the streaming limit above provides an upper bound on the allowed coupling and lower bound on the excluded coupling by considering purely production. Naively it might be expected that this suffices, that all higher couplings are excluded. However, in order to function as a cooling channel, obviously enough of the produced light gauge bosons must escape the supernova. As the coupling increases, so do processes that prevent this,and so the excluded region has an upper bound, above which the luminosity again drops below the neutrino luminosity. The first such limit may be found by considering decay of the dark bosons into Standard Model particles, and assuming that these SM particles are trapped in the supernova core and contribute nothing to the cooling. The dark boson has a typical lifetime of 
	\[ l = \frac{3 E_{A}}{N_{eff} m_A^2 \epsilon^2}  \]
	and so the fraction escaping the supernova is given by 
	\[ e^{\frac{r_{decay}}{l}} = e^{\frac{r_{decay} N_{eff} m_A^2 \epsilon^2}{3 E_A}} \] To take this into account, the above exponential factor is simply appended to the phase space integrand, and the calculation then proceeds as before. The limit is derived from the same equation, with the only complication being the fact that $ I_A $ is now a function of $ \epsilon $, in addition to $ m_A, T $. This makes the numerical calculation slightly more complicated, but otherwise changes nothing of importance. 
	 \[ \epsilon \le \sqrt{\frac{4.1 * 10^{37} MeV^2}{I_A(m_A, T, \epsilon)}} \]

	\subsection{Trapping limit}
	The second constraint that produces an upper bound on the excluded region comes from considering trapping of dark bosons within the supernova. With a large enough coupling, the new particles will thermalize and then be emitted from a spherical shell. In this case the luminosity is given simply by the Steffan-Boltzmann law
	\[ \mathcal{L}_t  = 4\pi r^2 T_A^4 \sigma\]
	where $ r $ is now the radius of the emitting shell and $ T_A $ its temperature. These must typically be calculated, but for $ r $ it is safe to assume a value of 10 km, since the density of the supernova drops drastically around that point. After taking that value for r, the bound on the luminosity translates into a bound on $ T_A $ \[ T_A \le 9.586 MeV \] That bound can then be translated into the desired bound on the coupling as a function of mass by assuming that the particles are emitted from an optical depth $ \tau = \frac{2}{3} $, and finding the temperature that corresponds to that optical depth. This is a somewhat involved calculation.
	First, one needs a model for the density and temperature in the supernova. Following \cite{dent}, we assume \[ \rho = \rho_p (\frac{R}{r})^2 \] \[ T = T_R (\frac{R}{r})^{n/3} \]
	with $  \rho_p  = 3*10^{14} g/cm^3, T_R = 30$ MeV, and taking $ n = 5 $. The optical depth is given by \[ \tau = \int_{r_x}^{\infty} \kappa \rho dr \]where $ \kappa is the opacity $. 
	To find the opacity, we start from the reduced mean Rosseland opacity \[ \frac{1}{\kappa \rho} = \int_{m_x}^{\infty} \frac{15}{4 \pi^4 T^5} \frac{E_A^2 e^{E_A/T} \sqrt{E_A^2 - m_A^2}}{(e^{E_A/T}-1)^2} l_A dE_A \]where $ l_A $ is the mean free path.

@@

%	\end{thebibliography}
\end{document}

>>>>

\documentclass[nofootinbib,aps,prd,preprint,superscriptaddress]{revtex4}
\usepackage{amsmath,graphicx,hyperref}
\usepackage{slashed}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Command %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\fms}[1]{{#1}\!\!\!/}
\newcommand{\fmsl}[1]{{#1}\!\!\!\!/}

\newcommand{\mc}{\mathcal}
\newcommand{\mr}{\mathrm}
\newcommand{\mP}{\mathcal{P}}
\newcommand{\mO}{\mathcal{O}}

\newcommand{\be}{\begin{equation}} 
\newcommand{\ee}{\end{equation}} 
\newcommand{\beq}{\begin{equation}} 
\newcommand{\eeq}{\end{equation}} 
\newcommand{\bea}{\begin{eqnarray}} 
\newcommand{\eea}{\end{eqnarray}}

\newcommand{\ov}{\overline}
\newcommand{\pp}{\perp}
\newcommand{\dg}{\dagger}
\newcommand{\n}{\overline{n}}
\newcommand{\nn}{\frac{\fms{\overline{n}}}{2}} 
\newcommand{\nnn}{\frac{\fms{n}}{2}}

\newcommand{\bl}[1]{{\bf{#1}}}
\newcommand{\bla}[1]{|{\bf{#1}}|}
\newcommand{\blp}[1]{{\bf{#1}}_{\perp}}
\newcommand{\blpu}[1]{{\bf{#1}}^{\perp}}
\newcommand{\blpa}[1]{|{\bf{#1}}_{\perp}|}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\bsp}[1]{{\boldsymbol{#1}}_{\perp}}

\newcommand{\ds}{\displaystyle} 
\newcommand{\nnb}{\nonumber}

\newcommand{\as}{\alpha_s}

\newcommand{\eps}{\epsilon} 
\newcommand{\veps}{\varepsilon}

\newcommand{\UV}{\veps_{\mr{UV}}}
\newcommand{\IR}{\veps_{\mr{IR}}}

\newcommand{\La}{\Lambda^2_{\rm{alg}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\topmargin 0.0 in

@@

\baselineskip 3.0ex

\vspace*{18pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Title?}

\def\Pitt{Pittsburgh Particle Physics Astrophysics and Cosmology Center (PITT PACC) \\ Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, Pennsylvania 15260, USA}

\author{Cameron Mahoney}
\email[E-mail:]{cbm34@pitt.edu}
\affiliation{\Pitt}
\author{Adam K. Leibovich}
\email[E-mail:]{akl2@pitt.edu}
\affiliation{\Pitt}
\author{Andrew R. Zentner}
\email[E-mail:]{zentner@pitt.edu}
\affiliation{\Pitt}

\begin{abstract} 
\baselineskip 3.0ex   
Abstract?
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Considering first the pp diagrams, each of the $p-p-\pi $ vertices contribute a factor of $ i\gamma_5 g_{pp}$ , where $g_{pp}$ is the pseudoscalar pion-nucleon coupling. $f_{pp}$, the pseudovector pion-nucleon coupling, is related by $ g_{pp} = \frac{2M_N}{m_\pi} f_{pp} $. The internal  pion line contributes a factor of $\frac{-i}{\mathcal{L}^2 - m_\pi^2}$, where $ \mathcal{L} $ is the appropriate exchange momentum.  The two outgoing nucleons each contribute a spinor $ \bar{u}(p_i)$, and the two incoming nucleons contribute a spinor $u(p_i)$. The outgoing boson A with momentum $q_a$ contributes a polarization vector $\epsilon^\mu$, and the $ p-p-A $ vertex contributes $e\epsilon \gamma_\mu$. The internal fermion line, between the $p-p-\pi$ vertex and the $p-p-A$ vertex, contributes a factor of 
\begin{equation} 
-i\frac{\slashed p_5 + M_N}{p_5^2-M^2_N},
\end{equation}
where $p_5$ is the momentum of the internal fermion. Considering diagram 2 as an example, we have $p_5 = q_a + p_3$, and so $p_5^2 = p_5 \cdot p_5 = q_a^2 + p_3^2 + 2 (q_a \cdot p_3)$, and the factor from the fermion line becomes 
\begin{equation}
-i\frac{\slashed p_i \pm \slashed q_a + M_N}{m_A^2 \pm 2 q_a \cdot p_i},
\end{equation}
where the index labels which of the nucleons attaches to the A boson, while the plus sign corresponds to diagrams where it attaches right of the pion vertex, and the minus to diagrams where it attaches left of the pion vertex. Labeling them from one to eight, with the exchange diagrams given odd labels and the direct given even labels, the matrix elements are then
\bea
M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed{\epsilon} u(p_1),\\
M_2 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p3) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed \epsilon  u(p_1), \\
M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \epsilon  u(p_2), \\
M_4 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \epsilon  u(p_2), \\
M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
			 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \slashed{\epsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
M_6 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \slashed{\epsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \slashed{\epsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),\\
M_8 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
		}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),
\eea
where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and $ f_{pp} $ is the pseudovector pion-nucleon coupling.

The amplitude is then 
\beq
\sum_{spins} \mathcal{M}^2 = \sum_{spins}|M_2+M_4+M_6+M_8-M_1-M_3-M_5-M_7|^2.
\eeq
At this point the calculation diverges from the axionic bremsstrahlung calculation: in the region of the mass of the A boson is not necessarily negligible. The kinematic relations are thus \bea 
p_1 \cdot p_2 &=& M_N^2 - \frac{l^2}{2} - \frac{k^2}{2} + p_2 \cdot q_a,\\
p_1 \cdot p_3 &=& M_N^2 + k \cdot l - \frac{k^2}{2} + p_3 \cdot q_a,\\  
p_1 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2}{2} + p_4 \cdot q_a, \\
p_2 \cdot p_3 &=& M_N^2 - \frac{l^2}{2}, \\
p_2 \cdot p_4 &=& M_N^2 - \frac{k^2}{2},\\
p_3 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2 + k^2}{2}
\eea
 Unfortunately, with these relations it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression contains some two hundred and fifty terms.

 For the pn interaction the calculation proceeds similarly, with the only new matrix element coming from diagram five, bremsstrahlung off the internal pion 
 \beq
 M_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \epsilon}{l^2-m_\pi^2
 	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \epsilon
\eeq
This amplitude too is unwieldy.

@@

\beq
Q_i = \int (2\pi)^4 E_A \sum_{spins} \mathcal{M}^2_i f(p_1) f(p_2)\delta(p_1+p_2-p_3-p_4-q_a) dLIPS.
\eeq
Here $ E_A $ is the energy of the emitted boson, and $ f(p) $ are the initial occupation numbers. The nucleons in the core are comfortably non-degenerate and non-relativistic, so  the Pauli blocking factor is omitted and the Maxwell-Boltzmann distribution used  
\beq
	f(p) =  \frac{n_b}{2} (\frac{2 \pi}{M_N T})^{3/2} e^{-\frac{\textbf{p}^2} {2 M_N T}}.
\eeq

This integration is performed numerically to obtain $ Q_i $, which is the rate of energy emission per unit volume associated with either the pn or pp process. To obtain the dark gauge boson luminosity, it is assumed that production takes place in a core volume of radius 1 km, so $ \mathcal{L}_A = V(Q_{pp} + Q_{pn}) $. $ \mathcal{L}_A $ is a complicated function of $ m_A $ and $ T $, but is simply proportional to the square of the parameter $ \epsilon $; pulling that out of the expression gives a constraint 
\beq
\epsilon^2 I_A(m_A, T) \le \mathcal{L}_\nu
\eeq
or a bound on the coupling of 
\beq 
\epsilon \le \sqrt{\frac{4.1 * 10^{37} MeV^2}{I_A(m_A, T)}} 
\eeq 
and the exclusion region is generated by varying the mass.

\subsection{Decay limit}
The constraint from the streaming limit above provides an upper bound on the allowed coupling and lower bound on the excluded coupling by considering purely production. Naively it might be expected that this suffices, that all higher couplings are excluded. However, in order to function as a cooling channel, obviously enough of the produced light gauge bosons must escape the supernova. As the coupling increases, so do processes that prevent this,and so the excluded region has an upper bound, above which the luminosity again drops below the neutrino luminosity. The first such limit may be found by considering decay of the dark bosons into Standard Model particles, and assuming that these SM particles are trapped in the supernova core and contribute nothing to the cooling. The dark boson has a typical lifetime of 
\beq
l = \frac{3 E_{A}}{N_{eff} m_A^2 \epsilon^2},
\eeq
and so the fraction escaping the supernova is given by 
\beq
e^{\frac{r_{decay}}{l}} = e^{\frac{r_{decay} N_{eff} m_A^2 \epsilon^2}{3 E_A}}.
\eeq
To take this into account, the above exponential factor is simply appended to the phase space integrand, and the calculation then proceeds as before. The limit is derived from the same equation, with the only complication being the fact that $ I_A $ is now a function of $ \epsilon $, in addition to $ m_A, T $. This makes the numerical calculation slightly more complicated, but otherwise changes nothing of importance. 
\beq
\epsilon \le \sqrt{\frac{4.1 * 10^{37} MeV^2}{I_A(m_A, T, \epsilon)}}.
\eeq

\subsection{Trapping limit}
The second constraint that produces an upper bound on the excluded region comes from considering trapping of dark bosons within the supernova. With a large enough coupling, the new particles will thermalize and then be emitted from a spherical shell. In this case the luminosity is given simply by the Steffan-Boltzmann law
\beq
\mathcal{L}_t  = 4\pi r^2 T_A^4 \sigma,
\eeq
where $ r $ is now the radius of the emitting shell and $ T_A $ its temperature. These must typically be calculated, but for $ r $ it is safe to assume a value of 10 km, since the density of the supernova drops drastically around that point. After taking that value for r, the bound on the luminosity translates into a bound on $ T_A $ 
\beq
T_A \le 9.586 MeV.
\eeq
That bound can then be translated into the desired bound on the coupling as a function of mass by assuming that the particles are emitted from an optical depth $ \tau = \frac{2}{3} $, and finding the temperature that corresponds to that optical depth. This is a somewhat involved calculation.
First, one needs a model for the density and temperature in the supernova. Following \cite{dent}, we assume 
\bea
\rho &=& \rho_p (\frac{R}{r})^2,\\
T &=& T_R (\frac{R}{r})^{n/3},
\eea
with $  \rho_p  = 3*10^{14} g/cm^3, T_R = 30$ MeV, and taking $ n = 5 $. The optical depth is given by 
\beq
\tau = \int_{r_x}^{\infty} \kappa \rho dr,
\eeq
where $ \kappa$ is the opacity.  To find the opacity, we start from the reduced mean Rosseland opacity 
\beq
\frac{1}{\kappa \rho} = \int_{m_x}^{\infty} \frac{15}{4 \pi^4 T^5} \frac{E_A^2 e^{E_A/T} \sqrt{E_A^2 - m_A^2}}{(e^{E_A/T}-1)^2} l_A dE_A,
\eeq
where $ l_A $ is the mean free path.

@@

%	\end{thebibliography}
\end{document}\acknowledgments

AKL was supported in part by NSF grant PHY-1519175.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{99}
%\normalsize

\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
